\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-11 k-planar.tex
minor updates

\note{DW}{We should be able to get treewidth 3 for $(g,1)$-planar graphs, combining the method in \cref{1-planar} with \citep{DHHW}}

@@

\note{DW}{We should be able to get treewidth 3 here using \cref{framed} and \citep{DHHW}.}

@@

\begin{cor}
\label{NewMapGraph}
Every $d$-map graph is contained in $H \boxtimes P \boxtimes K_{ d  \floor{d/2} }$ for some graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{cor}

@@

%%%%%%%%%%%%%%%%%%%%

The layering is in G_0. Each edge of G_2 has span at most floor(d/2)
with respect to this layering.

So G_2 is contained in H * P^{floor(d/2)} * K_d, which is contained in
H * P * K_{d floor(d/2) }.

>>>>

\note{DW}{I wonder if one can get treewidth 3 for $(g,1)$-planar graphs, combining the method in \cref{1-planar} with \citep{DHHW}. Perhaps this should be in another paper?}

@@

\note{DW}{I wonder if one can get treewidth 3 here using \cref{framed} and \citep{DHHW}. 
Perhaps this should be in another paper?}

@@

\begin{cor}
\label{NewMapGraph}
Every $d$-map graph is contained in $H \boxtimes P \boxtimes K_{ d + 3\floor{d/2} -3 }$ for some graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{cor}

@@
